### 2024-11-08 MetadataS1/tables/table_species_year_monitoring.tex
Reorganize scripts for extract species abundance
minor change table uncertainty intervals
version submitted to ecology - Data paper
update manuscrit data paper open research statement and minor changes lapland longspur and Baird sandpiper

% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Thu Oct  3 13:54:34 2024
\begin{table}[ht]
\centering
\caption{Summary of vertebrate species monitoring in the Bylot Island study area. In this paper, we excluded certain years for specific species due to reduced sampling efforts. As a result, duration of times series presented here may differ slightly from those in Gauthier et al. (2024b).} 
\label{table:table_species_year_monitoring}
\begingroup\fontsize{8pt}{10pt}\selectfont
\begin{tabularx}{\textwidth}{lllll}
  \hline
{\textbf{Species}} & {\textbf{Zone}} & {\textbf{Years}} & {\textbf{Number of years}} & {\textbf{Monitoring}} \\ 
  \hline
Pacific loon & Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Pacific loon & Whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Red-throated loon & Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Red-throated loon & Whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  King eider & Qarlikturvik (8 km2 plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Long-tailed duck & Qarlikturvik (8 km2 plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Cackling goose & Qarlikturvik valley & 2004-2019, 2022-2023 & (18) & systematic \\ 
  Cackling goose & Whole study area & 2017-2019, 2022-2023 & (5) & systematic \\ 
  Snow goose & Camp 2 & 1999-2019, 2023 & (22) & systematic \\ 
  Tundra swan & Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Tundra swan & Whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Rough-legged hawk & Qarlikt., Black \& South plat. & 2007-2019, 2022 & (15) & systematic \\ 
  Rough-legged hawk & Whole study area & 2013-2019, 2022 & (8) & systematic \\ 
  Peregrine falcon & Qarlikt., Black \& South plat. & 2007-2019, 2022 & (15) & systematic \\ 
  Peregrine falcon & Whole study area & 2013-2019, 2022  & (8) & systematic \\ 
  Snowy owl & Qarlikt., Black \& South plat. & 1996-2019, 2023 & (25) & systematic \\ 
  Snowy owl & Whole study area & 2012-2019, 2022-2023 & (10) & systematic \\ 
  Rock ptarmigan & Qarlikturvik (8 km2 plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Sandhill crane & Qarlikturvik (8 km2 plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Common-ringed plover & Whole study area & 2015-2017 & (3) & systematic \\ 
  Baird's sandpiper & Qarlikturvik (2 km2 plot) & 2005-2019, 2022-2023 & (17) & systematic \\ 
  Glaucous gull & Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Glaucous gull & Whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Long-tailed jaeger & South Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Parasitic jaeger & South Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Parasitic jaeger & Whole study area & 2009-2019, 2022 & (12) & opportunistic \\ 
  Common raven & Whole study area & 2013-2019, 2022 & (8) & systematic \\ 
  Lapland longspur & Qarlikturvik (2 km2 plot) & 2005-2019, 2022-2023 & (17) & systematic \\ 
  Nearctic brown lemming & Qarlikturvik (trapping grids) & 1995-2019, 2021-2022 & (27) & systematic \\ 
  Nearctic collared lemming & Qarlikturvik (trapping grids) & 1995-2019, 2021-2022 & (27) & systematic \\ 
  Ermine & Whole study area & 1993-2019 & (27) & opportunistic \\ 
  Arctic fox & Whole study area & 2008-2016 & (9) & systematic \\ 
   \hline
\end{tabularx}
\endgroup
\end{table}

>>>>

% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Fri Nov  8 08:10:03 2024
\begin{table}[ht]
\centering
\caption{Summary of vertebrate species monitoring in the Bylot Island study area. In this paper, we excluded certain years for specific species due to reduced sampling efforts. As a result, duration of times series presented here may differ slightly from those in Gauthier et al. (2024b).} 
\label{table:table_species_year_monitoring}
\begingroup\fontsize{8pt}{10pt}\selectfont
\begin{tabularx}{\textwidth}{lllll}
  \hline
{\textbf{Species}} & {\textbf{Zone}} & {\textbf{Years}} & {\textbf{Number of years}} & {\textbf{Monitoring}} \\ 
  \hline
Pacific loon & Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Pacific loon & Whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Red-throated loon & Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Red-throated loon & Whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  King eider & Qarlikturvik (8 km2 plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Long-tailed duck & Qarlikturvik (8 km2 plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Cackling goose & Qarlikturvik valley & 2004-2019, 2022-2023 & (18) & systematic \\ 
  Cackling goose & Whole study area & 2017-2019, 2022-2023 & (5) & systematic \\ 
  Snow goose & Camp 2 & 1999-2019, 2022-2023 & (23) & systematic \\ 
  Tundra swan & Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Tundra swan & Whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Rough-legged hawk & Qarlikt., Black \& South plat. & 2007-2019, 2022 & (15) & systematic \\ 
  Rough-legged hawk & Whole study area & 2013-2019, 2022 & (8) & systematic \\ 
  Peregrine falcon & Qarlikt., Black \& South plat. & 2007-2019, 2022 & (15) & systematic \\ 
  Peregrine falcon & Whole study area & 2013-2019, 2022  & (8) & systematic \\ 
  Snowy owl & Qarlikt., Black \& South plat. & 1996-2019, 2022-2023 & (26) & systematic \\ 
  Snowy owl & Whole study area & 2012-2019, 2022-2023 & (10) & systematic \\ 
  Rock ptarmigan & Qarlikturvik (8 km2 plot) & 2005-2019, 2022 & (16) & opportunistic \\ 
  Sandhill crane & South Qarlikturvik valley & 2004-2019, 2022 & (17) & opportunistic \\ 
  Common-ringed plover & Whole study area & 2015-2017 & (3) & systematic \\ 
  Baird's sandpiper & Qarlikturvik (2 km2 plot) & 2005-2019, 2022-2023 & (17) & systematic \\ 
  Glaucous gull & Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Glaucous gull & Whole study area & 2017-2019, 2022 & (4) & systematic \\ 
  Long-tailed jaeger & South Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Parasitic jaeger & South Qarlikturvik valley & 2004-2019, 2022 & (17) & systematic \\ 
  Parasitic jaeger & Whole study area & 2009-2019, 2022 & (12) & opportunistic \\ 
  Common raven & Whole study area & 2013-2019, 2022 & (8) & systematic \\ 
  Lapland longspur & Qarlikturvik (2 km2 plot) & 2005-2019, 2022-2023 & (17) & systematic \\ 
  Nearctic brown lemming & Qarlikturvik (trapping grids) & 1995-2019, 2021-2022 & (27) & systematic \\ 
  Nearctic collared lemming & Qarlikturvik (trapping grids) & 1995-2019, 2021-2022 & (27) & systematic \\ 
  American ermine & Whole study area & 1993-2019 & (27) & opportunistic \\ 
  Arctic fox & Whole study area & 2008-2016 & (9) & systematic \\ 
   \hline
\end{tabularx}
\endgroup
\end{table}

### 2024-11-08 MetadataS1/tables/table_summary_methods_and_abundance.tex
update manuscrit data paper open research statement and minor changes lapland longspur and Baird sandpiper

% Fri Oct 25 14:16:25 2024

@@

Snowy owl & Extrapolation from intensive nest monitoring (111 km2, R2=0.99, p$<$0.0001, n=10) & high & Strong correlation with study area-wide nest density &  &  &  &  & NA (1996-2011) \\ 

@@

Sandhill crane & Extrapolation from intensive nest monitoring (8 km2) and transect observations (R2= 0.44 p= 0.32, n=8) & moderate & Uncertain relation with large scale indices &  &  & 34* &  &  \\ 

@@

Ruddy turnstone & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 40* &  &  \\ 

@@

Ruddy turnstone & Derived from the abundance estimate of Bairds sandpiper using incidental observations & very low & Derived from moderate quality estimate of another species, but potentially includes transient migratory individuals &  &  & 53* &  &  \\ 

@@

Red knot & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 66* &  &  \\ 

@@

Red knot & Derived from the abundance estimate of Bairds sandpiper using incidental observations & very low & Derived from moderate quality estimate of another species, but potentially includes transient migratory individuals &  &  & 233* &  &  \\ 

@@

Pectoral sandpiper & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 80* &  &  \\ 

@@

Pectoral sandpiper & Derived from the abundance estimate of Bairds sandpiper using incidental observations & very low & Derived from moderate quality estimate of another species, but potentially includes transient migratory individuals &  &  & 255* &  &  \\ 

@@

Baird's sandpiper & Extrapolation from intensive nest monitoring (2 km2) and transects observations (R2=0.38, p=0.35, n=8) & moderate & Uncertain relation with large scale indices &  &  & 2448* &  &  \\ 

@@

White-rumped sandpiper & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 991* &  &  \\ 

@@

White-rumped sandpiper & Derived from the abundance estimate of Bairds sandpiper using incidental observations & very low & Derived from moderate quality estimate of another species, but potentially includes transient migratory individuals &  &  & 1134* &  &  \\ 

@@

Buff-breasted sandpiper & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 6* &  &  \\ 

@@

Buff-breasted sandpiper & Derived from the abundance estimate of Bairds sandpiper using incidental observations & very low & Derived from moderate quality estimate of another species, but potentially includes transient migratory individuals &  &  & 8* &  &  \\ 

@@

Red phalarope & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 140* &  &  \\ 

@@

Red phalarope & Derived from the abundance estimate of Bairds sandpiper using incidental observations & very low & Derived from moderate quality estimate of another species, but potentially includes transient migratory individuals &  &  & 270* &  &  \\ 

@@

Glaucous gull & Extrapolation from intensive nest monitoring (111 km2, R2=0.84, p=0.16, n=4) & high & Strong correlation with study area-wide nest density & 59* & 80* & 73* & 6 & 13 (2004-2016) \\ 

@@

Horned lark & Derived from the abundance estimate of Lapland longspur using transects observations & low & Derived from moderate quality estimate of another species &  &  & 362* &  &  \\ 

@@

Horned lark & Derived from the abundance estimate of Lapland longspur using incidental observations & low & Derived from moderate quality estimate of another species &  &  & 411* &  &  \\ 

@@

American pipit & Derived from the abundance estimate of Lapland longspur using transects observations & very low & Derived from moderate quality estimate of another species and prime nesting habitat not sampled &  &  & 53* &  &  \\ 

@@

American pipit & Derived from the abundance estimate of Lapland longspur using incidental observations & low & Derived from moderate quality estimate of another species and prime nesting habitat not well sampled &  &  & 87* &  &  \\ 

@@

Lapland longspur & Extrapolation from intensive nest monitoring (2 km2) and transects observations (R2=0.62, p=0.1, n=8) & moderate & Uncertain relation with large scale indices &  &  & 7110* &  &  \\ 

@@

Snow bunting & Derived from the abundance estimate of Lapland longspur using transects observations & very low & Derived from moderate quality estimate of another species and prime nesting habitat not sampled &  &  & 18* &  &  \\ 

@@

Snow bunting & Derived from the abundance estimate of Lapland longspur using incidental observations & low & Derived from moderate quality estimate of another species and prime nesting habitat not well sampled &  &  & 276* &  &  \\ 

>>>>

% Fri Nov  8 08:10:10 2024

@@

Snowy owl & Extrapolation from intensive nest monitoring (111 km2, R2=0.98, p$<$0.0001, n=10) & high & Strong correlation with study area-wide nest density & 0* & 67* & 15* & 24 & 16 (1996-2011) \\ 

@@

Sandhill crane & Intensive nest monitoring (33 km2) extrapolated to study area & moderate & Nest density is extrapolated uniformly across the study area &  &  & 36* &  &  \\ 

@@

Ruddy turnstone & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 36* &  &  \\ 

@@

Ruddy turnstone & Derived from the abundance estimate of Bairds sandpiper using incidental observations & very low & Derived from moderate quality estimate of another species, but potentially includes transient migratory individuals &  &  & 47* &  &  \\ 

@@

Red knot & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 59* &  &  \\ 

@@

Red knot & Derived from the abundance estimate of Bairds sandpiper using incidental observations & very low & Derived from moderate quality estimate of another species, but potentially includes transient migratory individuals &  &  & 206* &  &  \\ 

@@

Pectoral sandpiper & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 71* &  &  \\ 

@@

Pectoral sandpiper & Derived from the abundance estimate of Bairds sandpiper using incidental observations & very low & Derived from moderate quality estimate of another species, but potentially includes transient migratory individuals &  &  & 226* &  &  \\ 

@@

Baird's sandpiper & Extrapolation from intensive nest monitoring (2 km2) and transects observations & moderate & Uncertain relation between nest density and transects observations &  &  & 2170* &  &  \\ 

@@

White-rumped sandpiper & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 878* &  &  \\ 

@@

White-rumped sandpiper & Derived from the abundance estimate of Bairds sandpiper using incidental observations & very low & Derived from moderate quality estimate of another species, but potentially includes transient migratory individuals &  &  & 1005* &  &  \\ 

@@

Buff-breasted sandpiper & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 5* &  &  \\ 

@@

Buff-breasted sandpiper & Derived from the abundance estimate of Bairds sandpiper using incidental observations & very low & Derived from moderate quality estimate of another species, but potentially includes transient migratory individuals &  &  & 7* &  &  \\ 

@@

Red phalarope & Derived from the abundance estimate of Bairds sandpiper using transects observations & low & Derived from moderate quality estimate of another species &  &  & 124* &  &  \\ 

@@

Red phalarope & Derived from the abundance estimate of Bairds sandpiper using incidental observations & very low & Derived from moderate quality estimate of another species, but potentially includes transient migratory individuals &  &  & 240* &  &  \\ 

@@

Glaucous gull & Extrapolation from intensive nest monitoring (111 km2, R2=0.7, p=0.16, n=4) & high & Strong correlation with study area-wide nest density & 59* & 80* & 73* & 6 & 13 (2004-2016) \\ 

@@

Horned lark & Derived from the abundance estimate of Lapland longspur using transects observations & low & Derived from moderate quality estimate of another species &  &  & 310* &  &  \\ 

@@

Horned lark & Derived from the abundance estimate of Lapland longspur using incidental observations & low & Derived from moderate quality estimate of another species &  &  & 352* &  &  \\ 

@@

American pipit & Derived from the abundance estimate of Lapland longspur using transects observations & very low & Derived from moderate quality estimate of another species and prime nesting habitat not sampled &  &  & 46* &  &  \\ 

@@

American pipit & Derived from the abundance estimate of Lapland longspur using incidental observations & low & Derived from moderate quality estimate of another species and prime nesting habitat not well sampled &  &  & 74* &  &  \\ 

@@

Lapland longspur & Extrapolation from intensive nest monitoring (2 km2) and transects observations & moderate & Uncertain relation between nest density and transects observations &  &  & 6080* &  &  \\ 

@@

Snow bunting & Derived from the abundance estimate of Lapland longspur using transects observations & very low & Derived from moderate quality estimate of another species and prime nesting habitat not sampled &  &  & 15* &  &  \\ 

@@

Snow bunting & Derived from the abundance estimate of Lapland longspur using incidental observations & low & Derived from moderate quality estimate of another species and prime nesting habitat not well sampled &  &  & 236* &  &  \\ 
